### 2024-03-29 paper.tex
review

\usepackage{amsmath,amsthm,amssymb,amsfonts}

@@

\englishTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data Collection and Analysis}

@@

\portugueseTitle{Explorando a Dinâmica dos Raios e seus Efeitos Térmicos: Insights a partir da Coleta e Análise de Dados}

@@

The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms. The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions \citeapud{Pimenta1987}{Torrens1992}{46}.

@@

  \vspace{-3mm} 
  \begin{center}
    \includegraphics[bb=0 0 2632 1814, width=0.55\textwidth, trim={0 0 0 0},clip]{author_files/14-bis.jpeg}
  \end{center}

@@

  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons}

@@

  The Electroplumbus Nimbodetector undergoes rigorous calibration and validation processes to ensure accurate and reliable measurements. Prior to deployment, the device is calibrated against reference instruments and tested under controlled laboratory conditions to establish its performance characteristics. Special attention is given to the sensitivity, precision, and response time of the sensor and thermometer to ensure the accurate capture of data during lightning strikes.

@@

  \begin{center}
    \vspace{-3mm}

@@

  \end{center}%

@@

\vspace{-5mm}

@@

\begin{center}

@@

  \end{tabular}\\[3mm]
\end{center}

@@

\end{table}
\vspace{-6mm}

@@

  \vspace{-3mm} 
  \begin{center}
    \includegraphics[bb=0 0 700 524, width=0.85\textwidth, trim={0 0 0 0},clip]{author_files/graph.png}
  \end{center}

>>>>

\usepackage{amsthm,amssymb,amsfonts}

@@

\englishTitle{Exploring the dynamics of lightning and its thermal effects: Insights from Data collection and analysis}

@@

\portugueseTitle{Explorando a dinâmica dos raios e seus efeitos térmicos: Percepções a partir da coleta e análise de dados}

@@

The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms. The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions \citeapud{Pimenta1987}{Torrens1992}{46}.\par

@@

  \includegraphics[bb=0 0 2632 1814, width=0.55\textwidth, trim={0 0 0 0},clip]{author_files/14-bis.jpeg}\\

@@

    Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons

@@

  The Electroplumbus Nimbodetector undergoes rigorous calibration and validation processes to ensure accurate and reliable measurements. Prior to deployment, the device is calibrated against reference instruments and tested under controlled laboratory conditions to establish its performance characteristics. Special attention is given to the sensitivity, precision, and response time of the sensor and thermometer to ensure the accurate capture of data during lightning strikes.\par

@@

@@

@@

@@

@@

  \end{tabular}\\

@@

\end{table}\par

@@

  \includegraphics[bb=0 0 700 524, width=0.85\textwidth, trim={0 0 0 0},clip]{author_files/graph.png}\\
